---
title: "Skew-T & Group-T Copula"
author: "I-Lun Tu"
date: "4/26/2022"
output:
  slidy_presentation: default
  df_print: kable
  beamer_presentation: null
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(sn)
library(MASS)
library(ghyp)
library(astsa)
library(tidyverse)
library(EnvStats)
library(numDeriv)
library(signal)
library(mnormt)
library(sn)
library(MASS)
library(ghyp)
library(knitr)
```

## Content
- Research Motivation and Possible Contribution
- Skew-T Copula and Group-T Copula
- Copula Estimation Process
- Application to Financial Data
- Unconditional Coverage of VaR
- Possible Improvement

## Research Motivation and Possible Contribution
- Straightforward way to generalize copula to higher dimensions
  - More parsimonious model than Vine based Copula
  - Easier Interpretation - shape, dispersion, and skewness
  - Bivariate Student-T is effective for pairs of stocks

- Captures stylized facts of financial markets
  - Asymptotic tail dependence
  - Asymmetry - joint lower-tailed events

- Empirical results to support skew-T Copula in market risk
  - One-stage estimation usually does not select skew-T over standard T
  - Modern unconditional tests for tail risk model
  - High computational costs and accuracy of skewness parameter

## Skew-T Copula and Group-T Copula
- Skew-T Distribution:
$$X=\mathbf{\gamma} V^{-1} + V^{-\frac{1}{2}}\mathbf{Z}$$
where $V$ is $G(\frac{\nu}{2},\frac{\nu}{2})$, $\mathbf{\gamma}$ is skewness parameter vector.
  - General Hyperbolic Distribution - Normal mean-variance mixture distribution
  - When $\gamma=0$, it reduces to Student-T distribution
  - When $\nu\to\infty$, it becomes Normal distribution (not skew Normal)
  - $\nu>4$ to have finite covariance - difficulty in application

- Skew-T Copula:
$$C^{t}_{\nu, P, \gamma}$$
where $P$ is the correlation matrix.
  - Same copula for different dispersion and location  
  - Different $\nu,\gamma$ to form skew and group copula (generalized T) 

## Skew-T Copula and Group-T Copula
```{r,echo=F,fig.width=7,out.width = '80%',fig.align='center'}
## Data Generation
set.seed(5)
sigma_1<- var(matrix(rt(120,df=5),ncol=2))
sigma_2<- matrix(c(1,0.6,0.6,1),nrow = 2)

generation<- ghyp(lambda = -0.5*5,chi = 5,psi = 0,mu=c(0,0),sigma = sigma_2,gamma = c(-0.8,0.8),alpha.bar = 0)
skew_t<- rghyp(10000,object = generation)

## Plotting Copula
marginal_1<- ghyp(lambda = -0.5*5,chi = 5,psi = 0,mu=0,sigma = 1,gamma = -0.8,alpha.bar = 0)
marginal_2<- ghyp(lambda = -0.5*5,chi = 5,psi = 0,mu=0,sigma = 1,gamma = 0.8,alpha.bar = 0)
copula_1<- pghyp(skew_t[,1],object = marginal_1)
copula_2<- pghyp(skew_t[,2],object = marginal_2)
plot(copula_1,copula_2,pch=1, xlab="", ylab="",main="Different Skewness")
```

## Copula Estimation Process
- Two Stage Estimation:
  - Forming pseudo observations from the copula
    - Parametric estimation
    - Non-parametric estimation (empirical distribution function)
  - Maximum likelihood estimation for the copula parameters

- Difficulty:
  - When maximizing copula density, marginal quantile functions have to be calculated $n*d$ times
    - No close form quantile function for univariate skew-T
    - Empirical quantile functions has to be simulated for a large number
  - Positive semi-definiteness of the correlation matrix is not guaranteed
    - Empirical correlation using Kendall's tau might not work
- Recent Advancement (Toshinao Yoshiba 2018):
  - Monotone interpolator (100 interpolating quantiles)  
  - Reparameterize the Cholesky decomposed triangular matrix with trigonometric functions

## Application to Financial Data
- Establish VaR for stock portfolio on financial institution
  - Consumer finance, commercial banking, brokerage and investment management
  - Dependence modelling for 15 stocks (5 each) equal weight portfolio
  - Simulate VaR to set up threshold for loss distribution
  - Measure the dependence structure

## Application to Financial Data
### Copula Estimation Process
  - Data Preprocess: unfiltered 5 years weekly log-returns for stocks (serial uncorrelated)
  
  - Pseudo copula observations: nonparametric estimation 
    $\frac{1}{n+1}\sum_{t = 1}^{n}I_{(X_{t,i<=x})}$ (McNeil 2015)
    
  - Copula estimation: use the recently proposed method to estimate $\nu,\gamma,P$ (equal-skewness)
  
## Application to Financial Data
### Pseudo Copula

```{r,echo=FALSE}
# Empirical
## Data
Banking_1<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Banking\\Bac.csv")
Banking_2<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Banking\\C.csv")
Banking_3<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Banking\\PNC.csv")
Banking_4<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Banking\\USB.csv")
Banking_5<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Banking\\WFC.csv")

Brokerage_1<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Brokerage & Investment\\BLK.csv")
Brokerage_2<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Brokerage & Investment\\ICE.csv")
Brokerage_3<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Brokerage & Investment\\MS.csv")
Brokerage_4<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Brokerage & Investment\\SCHW.csv")
Brokerage_5<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Brokerage & Investment\\SPGI.csv")

Consumer_1<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Consumer Finance\\AXP.csv")
Consumer_2<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Consumer Finance\\INTU.csv")
Consumer_3<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Consumer Finance\\MA.csv")
Consumer_4<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Consumer Finance\\COF.csv")
Consumer_5<- read.csv("C:\\Users\\absur\\Desktop\\Pis\\[2] UIUC\\[1] Courses\\[3] Spring 2022\\Math 563\\Project\\Data\\Consumer Finance\\V.csv")

Banking<- cbind(Banking_1[,5],Banking_2[,5],Banking_3[,5],Banking_4[,5],Banking_5[,5])
Brokerage<-cbind(Brokerage_1[,5],Brokerage_2[,5],Brokerage_3[,5],Brokerage_4[,5],Brokerage_5[,5])
Consumer<-cbind(Consumer_1[,5],Consumer_2[,5],Consumer_3[,5],Consumer_4[,5],Consumer_5[,5])


Banking_log_return<-matrix(0,ncol = 5,nrow = nrow(Banking_1)-1)
Brokerage_log_return<-matrix(0,ncol = 5,nrow = nrow(Banking_1)-1)
Consumer_log_return<-matrix(0,ncol = 5,nrow = nrow(Banking_1)-1)

for (i in 1:5){
  Banking_log_return[,i]<-diff(log(Banking[,i]))
  Brokerage_log_return[,i]<-diff(log(Brokerage[,i]))
  Consumer_log_return[,i]<-diff(log(Consumer[,i]))
}

Data_log_return<- cbind(Banking_log_return,Brokerage_log_return,Consumer_log_return)

### Non-parametric
edf<-function(x,obs){
  n<-length(obs)
  
  indicator<- 0
  for (i in 1:n){
    if (x>=obs[i]){
      indicator<-indicator+1
    }
  }
  return((n+1)^(-1)*indicator)
}

### Non-Parametric Pseudo Copula
pseudo_copula_matrix<- copula_matrix<- matrix(0,ncol = 15,nrow = nrow(Data_log_return))
for (i in 1:15){
  for (j in 1:nrow(Data_log_return)){
    pseudo_copula_matrix[j,i]<-edf(Data_log_return[j,i],Data_log_return[,i])
  }
}

pairs(pseudo_copula_matrix[,1:5],main="Banking Portfolio")

```

## Application to Financial Data
### Copula Estimation 

- Substantial improvement in log-likelihood
- Skewness parameter is warranted

```{r,echo=FALSE,fig.height = 5, fig.width = 5, out.width = '50%', fig.align = "center"}
## rho vector to Omega matrix ##
rhoToOmega <- function(rho){
  dim <- (sqrt(8*length(rho)+1)+1)/2;
  Omega <- diag(1/2,dim);
  Omega[lower.tri(Omega)] <- rho;
  Omega <- Omega + t(Omega);
  Omega;
}

## transforming original parameters to internal parameters ##
GHEstIntPara <- function(rho,gamma,nu){
  R <- rhoToOmega(rho);
  LTR <- t(chol(R));
  dim <- nrow(LTR);
  theta <- acos(LTR[2:dim,1]);
  cumsin <- sin(theta)[-1];
  if(dim>2){
    for(j in 2:(dim-1)){
      thj <- acos(LTR[(j+1):dim,j]/cumsin);
      theta <- c(theta,thj);
      cumsin <- (cumsin*sin(thj))[-1];
    }
  }
  c(theta,gamma,log(nu-2.0));
}

## transforming internal parameters to original parameters ##
GHEstOrgPara <- function(para){
  ntheta <- length(para)-2;
  dim <- (1+sqrt(1+8*ntheta))/2;
  theta <- para[1:ntheta];
  LTR <- diag(dim);
  LTR[-1,1] <- cos(theta[1:(dim-1)]);
  cumsin <- sin(theta[1:(dim-1)]);
  if(dim>2){
    for(j in 2:(dim-1)){
      LTR[j,j] <- cumsin[1];
      k <- (j-1)*(dim-j/2)+1;
      thj <- theta[k:(k+dim-j-1)];
      cumsin <- cumsin[-1];
      LTR[((j+1):dim),j] <- cumsin*cos(thj);
      cumsin <- cumsin*sin(thj);
    }
  }
  LTR[dim,dim] <- cumsin[1];
  Omega <- LTR %*% t(LTR);
  gamma <- para[ntheta+1];
  nu <- exp(para[ntheta+2])+2.0;
  list(rho = Omega[lower.tri(Omega)], gamma = gamma, nu = nu);
}

## negative log-likelihood for GH skew-t copula
GHEstcopnll <- function(para, udat=NULL, mpoints=150){
  dim <- ncol(udat);
  dp <- GHEstOrgPara(para);
  gamma <- dp$gamma;
  nu <- dp$nu;
  ix <- ipqsGHEst(udat,gamma,nu,mpoints=mpoints);
  ## Activate the following line instead of monotone interpolating
  quantile
  ## function ipqsGHst() to use accurate quantile function aqsGHst()
  ## ix <- aqsGHst(udat,gamma,nu);
  ughyp <- ghyp(lambda=-nu/2, chi=nu, psi=0, sigma=1, gamma=gamma);
  lm <- dghyp(as.vector(ix), ughyp, logvalue=TRUE);
  mu <- rep(0,dim);
  mgamma <- rep(gamma,length=dim);
  mghyp <- ghyp(lambda=-nu/2, chi=nu, psi=0, mu=mu,
                sigma=rhoToOmega(dp$rho), gamma=mgamma);
  lc <- dghyp(matrix(ix,ncol=dim), mghyp, logvalue=TRUE);
  -sum(lc)+sum(lm)
}

## MLE for GH skew-t copula using optim
GHEstcop.mle <- function (udat = NULL, start = NULL, method = "Nelder-
Mead", mpoints=150, ...){
  iniPar <- GHEstIntPara(start$rho,start$gamma,start$nu);
  fit <- optim(iniPar, GHEstcopnll, method=method, hessian=FALSE,
               udat=udat, mpoints=mpoints, ...);
  list(call = match.call(), dp = GHEstOrgPara(fit$par), logL = -fit$value,
       details=fit, nobs = nrow(udat), method = method);
}

## interpolating quantiles for (equi-gamma) GH skew-t
ipqsGHEst <- function(udat,gamma,nu,mpoints=150){
  minmaxu <- c(min(udat),max(udat));
  ughyp <- ghyp(lambda=-nu/2, chi=nu, psi=0, sigma=1, gamma=gamma);
  minmaxx <- qghyp(minmaxu, ughyp, method = "splines");
  xx <- seq(minmaxx[1],minmaxx[2],length.out=mpoints);
  px <- sort(pghyp(xx, ughyp));
  ix <- pchip(px, xx, as.vector(udat));
  matrix(ix,nrow=nrow(udat),ncol=ncol(udat));
}


## t copula
tIntTPara <- function(rho,nu){
  R <- rhoToOmega(rho);
  LTR <- t(chol(R));
  ndim <- nrow(LTR);
  theta <- acos(LTR[2:ndim,1]);
  cumsin <- sin(theta)[-1];
  if(ndim>=3){
    for(j in 2:(ndim-1)){
      thj <- acos(LTR[(j+1):ndim,j]/cumsin);
      theta <- c(theta,thj);
      cumsin <- (cumsin*sin(thj))[-1];
    }
  }
  c(theta,log(nu-2.0));
}

tOrgTPara <- function(tpara){
  ntpara <- length(tpara);
  eta <- tpara[ntpara];
  theta <- tpara[-ntpara];
  ntheta <- length(theta);
  ndim <- (1+sqrt(1+8*ntheta))/2;
  LTR <- diag(ndim);
  LTR[-1,1] <- cos(theta[1:(ndim-1)]);
  cumsin <- sin(theta[1:(ndim-1)]);
  if(ndim>=3){
    for(j in 2:(ndim-1)){
      LTR[j,j] <- cumsin[1];
      k <- (j-1)*(ndim-j/2)+1;
      thj <- theta[k:(k+ndim-j-1)];
      cumsin <- cumsin[-1];
      LTR[((j+1):ndim),j] <- cumsin*cos(thj);
      cumsin <- cumsin*sin(thj);
    }
  }
  LTR[ndim,ndim] <- cumsin[1];
  Omega <- LTR %*% t(LTR);
  nu <- exp(eta)+2.0;
  list(rho = Omega[lower.tri(Omega)], nu = nu);
}

## t copula
tIntTPara <- function(rho,nu){
  R <- rhoToOmega(rho);
  LTR <- t(chol(R));
  ndim <- nrow(LTR);
  theta <- acos(LTR[2:ndim,1]);
  cumsin <- sin(theta)[-1];
  if(ndim>=3){
    for(j in 2:(ndim-1)){
      thj <- acos(LTR[(j+1):ndim,j]/cumsin);
      theta <- c(theta,thj);
      cumsin <- (cumsin*sin(thj))[-1];
    }
  }
  c(theta,log(nu-2.0));
}

## negative log-density for t copula
tcopnll <- function(tpara, udat=NULL){
  dp <- tOrgTPara(tpara);
  Omega <- rhoToOmega(dp$rho);
  nu <- dp$nu;
  dim <- ncol(udat);
  ax <- qt(udat, df=nu);
  lm <- dt(ax, df=nu, log=TRUE);
  lc <- dmt(matrix(ax,ncol=dim),S=Omega,df=nu,log=TRUE);
  -sum(lc)+sum(lm)
}

empirical_copula<- pseudo_copula_matrix
dim<- ncol(empirical_copula)

iniTdp <- list(rho=numeric(dim*(dim-1)/2),nu=6);
fit<-optim(tIntTPara(iniTdp$rho,iniTdp$nu), tcopnll,
           udat=empirical_copula, control=list(reltol=1e-4))
tdp <- tOrgTPara(fit$par);
tcopmle <- list(inidp = iniTdp, dp = tdp, logL = -fit$value,
                npara = length(fit$par), details=fit);



iniSTdp1 <- list(rho=tdp$rho,gamma=0,nu=tdp$nu);
iniSTPar <- GHEstIntPara(iniSTdp1$rho,iniSTdp1$gamma,iniSTdp1$nu);
fit<-optim(iniSTPar, GHEstcopnll, udat=empirical_copula,control=list(reltol=1e-4))
gstcopmle1 <- list(inidp = iniSTdp1, dp = GHEstOrgPara(fit$par), logL = -
                     fit$value, npara = length(fit$par), details=fit)
gstcopmle <- gstcopmle1

iniSTdp2 <- list(rho=numeric(dim*(dim-1)/2),gamma=0,nu=6);
iniSTPar <- GHEstIntPara(iniSTdp2$rho,iniSTdp2$gamma,iniSTdp2$nu);
fit<-optim(iniSTPar, GHEstcopnll, udat=empirical_copula,control=list(reltol=1e-4))
gstcopmle2 <- list(inidp = iniSTdp2, dp = GHEstOrgPara(fit$par), logL = -
                     fit$value, npara = length(fit$par), details=fit);
if(gstcopmle2$logL > gstcopmle$logL){ gstcopmle <- gstcopmle2; }

#### Comparison
log_lik<- c(tcopmle$logL,gstcopmle$logL)
nu<- c(tcopmle$dp$nu,gstcopmle$dp$nu)
gamma<- c(NA,gstcopmle$dp$gamma)
AIC<- c(-2*tcopmle$logL+2*tcopmle$npara,-2*gstcopmle$logL+2*gstcopmle$npara)
BIC<- c(-2*tcopmle$logL+log(nrow(Data_log_return))*tcopmle$npara,-2*gstcopmle$logL+log(nrow(Data_log_return))*gstcopmle$npara)
results<- rbind(nu,gamma,log_lik,AIC,BIC)
colnames(results)<- c("T-copula","Skew-T copula")
kable(results)

```

## Application to Financial Data
### Copula Estimation - copula

```{r,fig.height = 6, fig.width = 8, out.width = '100%', fig.align = "center"}
### GH skew-t
#### random number generator of GH skew-t copula
rGHEstcop <- function(n,rho,gamma,nu){
  vv <- if(nu==Inf) 1 else rchisq(n,nu)/nu;
  Omega <- rhoToOmega(rho);
  d <- nrow(Omega);
  z <- matrix(rnorm(n*d), n, d) %*% chol(Omega);
  gammaMat <- t(matrix(gamma, d, n));
  x <- gammaMat/vv + z/sqrt(vv);
  ughyp <- ghyp(lambda=-nu/2, chi=nu, psi=0, sigma=1, gamma=gamma);
  u <- matrix(pghyp(as.vector(x), ughyp),n,d);
  list(x=x,u=u);
}

generated_u<-rGHEstcop(500,gstcopmle$dp$rho,gstcopmle$dp$gamma,gstcopmle$dp$nu)
pairs(generated_u$u[,1:5],main="Banking Portfolio")

```


## Application to Financial Data
### Copula Simulation - Aggregate Loss

```{r,echo=FALSE,cache=TRUE}
generated_rv<-rGHEstcop(100000,gstcopmle$dp$rho,gstcopmle$dp$gamma,gstcopmle$dp$nu)
density(apply(scale(generated_rv$x),MARGIN = 1,mean)) %>% plot(xlim=c(-3,2),ylim=c(0,3),main="",lwd=2)

density(apply(scale(Data_log_return),MARGIN = 1,mean)) %>% lines(col="deepskyblue", lwd=2)

legend("topleft", c("actual", "estimated"), lty = 1, lwd = 2, col = c("deepskyblue", "black"))
```

## Application to Financial Data
### In-sample Testing for Aggregate Weekly Loss

```{r,echo=FALSE,cache=TRUE}
quantile<- sort(apply(scale(generated_rv$x),MARGIN = 1,mean))[c(1000,5000,10000,15000)]
empirical_1<- sum(apply(scale(Data_log_return),MARGIN = 1,mean) < quantile[1])/ nrow(Data_log_return)
empirical_2<- sum(apply(scale(Data_log_return),MARGIN = 1,mean) < quantile[2])/ nrow(Data_log_return)
empirical_3<- sum(apply(scale(Data_log_return),MARGIN = 1,mean) < quantile[3])/ nrow(Data_log_return)
empirical_4<- sum(apply(scale(Data_log_return),MARGIN = 1,mean) < quantile[4])/ nrow(Data_log_return)
VaR<- c("99%","95%","90%","85%")
empirical<- c(empirical_1,empirical_2,empirical_3,empirical_4)
results<-rbind(round(quantile,2),round(empirical,2))
colnames(results)<- c("99%","95%","90%","85%")
rownames(results)<-c("% VaR","Empirical Violation Percentage")
kable(results)
```

## Application to Financial Data
### One Stage EM Estimation

```{r}
mkPseudoDat <- function(orgdat){
  dim <- ncol(orgdat);
  N <- nrow(orgdat);
  u <- x <- matrix(0,nrow=N,ncol=dim);
  for(j in 1:dim){
    x[,j] <- orgdat[,j];
    Fx <- ecdf(x[,j]);
    u[,j] <- Fx(x[,j])*N/(N+1);
  }
  list(x=x,u=u);
}
fitted_2<- fit.tmv(Data_log_return,silent=T)
simulation_3<- rghyp(500,object = fitted_2)
pairs(mkPseudoDat(simulation_3)$u[,1:5])
```


## Application to Financial Data
### One Stage EM Estimation

```{r,echo=FALSE,message=FALSE,warning=FALSE,cache=TRUE}
### Multivariate skew-T
fitted_2<- fit.tmv(Data_log_return,silent=T)
simulation_2<- rghyp(100000,object = fitted_2)

density(apply(simulation_2,MARGIN = 1,mean)) %>% plot(ylim=c(0,20),main="",lwd=2)

density(apply(Data_log_return,MARGIN = 1,mean)) %>% lines(col="deepskyblue",lwd=2)

legend("topleft", c("actual", "estimated"), lty = 1, lwd = 2, col = c("deepskyblue", "black"))

```

## Application to Financial Data
### In-sample Testing for Aggregate Weekly Loss

```{r,echo=FALSE}
quantile<- sort(apply(simulation_2,MARGIN = 1,mean))[c(1000,5000,10000,15000)]
empirical_1<- sum(apply(Data_log_return,MARGIN = 1,mean) < quantile[1])/ nrow(Data_log_return)
empirical_2<- sum(apply(Data_log_return,MARGIN = 1,mean) < quantile[2])/ nrow(Data_log_return)
empirical_3<- sum(apply(Data_log_return,MARGIN = 1,mean) < quantile[3])/ nrow(Data_log_return)
empirical_4<- sum(apply(Data_log_return,MARGIN = 1,mean) < quantile[4])/ nrow(Data_log_return)
empirical<- c(empirical_1,empirical_2,empirical_3,empirical_4)
results<-rbind(round(quantile,2),round(empirical,2))
rownames(results)<-c("% VaR","Empirical Violation Percentage")
colnames(results)<- c("99%","95%","90%","85%")
kable(results)
```

## Possible Improvement
  - Omission of skewness information on pseudo copula
  - $\nu$ is close to boundary - group-T copula construction
  - Semi-parametric estimation on the marginals
  - Dynamic P&L and VaR modeling through t-Garch models
  - More comprehensive backtesting methods - Risk Map

## Reference
- McNeil, A. J., R. Frey, and P. Embrechts (2015) Quantitative Risk Management: Concepts, Techniques, and Tools, Princeton University Press, revised ed
- Demarta, S. and A. J. McNeil (2005) “The t copula and related copulas,” International Statistical Review, 73(1), 111–129.
- Toshinao Yoshiba Maximum likelihood estimation of skew- t copulas with its applications to stock returns May 2018 Journal of Statistical Computation and Simulation 88(2):1-18
- Colletaz, G., Hurlin, C. and Perignon, C. (2013). The risk map: A new tool for validating risk models. Journal of Banking and Finance, 37, 3843-3854






